---
title: "Alex Meeting"
author: "Blain Morin"
date: "4/14/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(tidyverse)
library(ctsem)
library(rstan)
library(plotly)
library(RColorBrewer)
library(gridExtra)

```


```{r}

fed = read.csv("https://www.dropbox.com/s/wlhuq8mdyidxdk3/fed_agency_capacity_autonomy.csv?dl=1")

agy_types = unique(fed$agy_typ)[unique(fed$agy_typ) != "TOTAL"]

top.level = paste0(unique(fed$agy_code), "00")

appendage = fed %>%
    select(agy_code, AGYSUB, yr, appt_pct, advs_pct, expert_pct) %>%
    filter(AGYSUB %in% top.level) %>%
    select(-AGYSUB) %>%
    rename(top_appt_pct = appt_pct, 
           top_advs_pct = advs_pct,
           top_expert_pct = expert_pct)

fed = fed %>%
    left_join(appendage)


drop.agy = fed %>%
    group_by(yr, agy_code) %>%
    summarise(n_in_code = n()) %>%
    filter(n_in_code > 1)

drop.agy = paste0(unique(drop.agy$agy_code), "00")

fed = fed %>%
    filter(!AGYSUB %in% drop.agy) %>%
    filter(!agy_full == "Dept. of Defense") %>%
    filter(AGYSUB != "TOTL") %>% ### Removes Total Rows 
    filter(!grepl("NET", agy_full))

all_agencies = unique(fed$agy_full)

### Set Seed
set.seed(3710)


# Choose Year Range
startyear = 1981 # Needs to be >=1974
endyear = 2010 # Needs to be <=2019

# Choose Agency Type
agencytype = agy_types[!agy_types %in% c("National Defense",
                               "Interest")]

# Choose Manifest Variables 
regressors = c("appt_pct",  "advs_pct", "top_appt_pct", "top_advs_pct", "b18_dng_r",
               "logn", "logb18",
               "med_sal_", "LOSavg", "ma_pct")
# names(fed)

# Choose Minimum Employee Size
minemployee = 3000

temp = fed %>%
            filter(n >= minemployee) %>%
            filter(yr %in% years) %>%
            filter(agy_typ %in% agencytype)
        
inc = unique(temp$agy_full)

# Data Clean
df = fed %>%
  filter(yr >= 1974) %>%
  filter(med_sal_ > 0) %>% 
  filter(agy_full %in% inc) %>%
  drop_na(med_sal_) %>% ### Am dropping NA here, but may not need to with ctsem
  filter(AGYSUB != "TOTL") %>% ### Removes Total Rows 
  filter(!grepl("NET", agy_full)) ### Removes any total agency counts, ie only individual agencies are left

# Data Process
years = startyear:endyear
dff = df %>%
  mutate(logn = log(n + 1)) %>%
  mutate(logb18 = log(b18 + 1)) %>%
  filter(agy_typ %in% agencytype) %>%
  filter(yr %in% startyear:endyear) %>%
  select(regressors, yr, AGYSUB, agy_full) %>%
  filter_at(vars(b18_dng_r), all_vars(!is.infinite(.))) %>%
  mutate_at(regressors, scale) %>%
  drop_na() 


```

# Recap

* We are interested using administrative data to model the latent capacity of federal agencies over time.
  * *Capacity:* Ability of the state to induce residents, firms and organizations to act in ways they would other wise not. 

* Data: Individual-level employment data from all federal agencies over the past 40 years
  * Group these observations to the agency-year to get measures such as % of employees with a master’s
degree or higher or average length of service (*our manifest variables*).


